Data Preparation

### 2019-03-11 Data Preparation.Rmd
remove words occuring only once or twice in the corpus

  data %>%
    anti_join(
      stop_words,
      by = "word"
      ) %>%
    anti_join(
      sw_own,
      by = "word"
      ) %>%
    filter(
      nchar(word) > 2
      )

>>>>

  data %>%
    anti_join(
      stop_words,
      by = "word"
      ) %>%
    anti_join(
      sw_own,
      by = "word"
      ) %>%

    # remove words of 1 or 2 letters
    filter(
      nchar(word) > 2
      ) %>%

    # Remove words occuring once or twice in corpus (usually names, website links or typos)
    add_count(word) %>%
    filter(n > 2) %>%
    select(-n)
